---
title: "spink1-prss1"
author: "Dongni Fu, Brandon M Blobner & Phil J Greer"
date: '2022-05-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plyr)
library(DescTools)
library(Publish)
library(gdata)
library(knitr)

options(scipen=1, digits=2)
```

## Data Import 

Reading in the combined pheotype and genotype (SPINK1 & PRSS1) data for all NAPS2 subjects.

Each genotype line is marked as counts of the minor allele in the column name. 0 = homozygous reference, 1 = heterozygous, 2 = homozygous minor allele.

```{r red_and_recode_data}

naps2_spink1_prss1 <- read.table("naps2_spink1_prss1.txt", header = TRUE)

```


## Demographic Table  Table 1

Build univariate demographics table.


```{r demo_tables }


## NAPS2 only

publish(univariateTable(phenotype ~ age + sex_cat + bmi_current + factor(diagnosis) + factor(rs17107315_C) +  factor(rs10273639_T)  , 
                        data=naps2_spink1_prss1,  compare.groups=TRUE,digits.summary=5 ),pvalue.digits = 10)

```


## Tables and fisher's test
Main table is pancreatitis vs control
Fishers exact test onresults of this table

Extra table printed for RAP, CP breakdown
```{r table4, echo=TRUE}

naps2_panc_con.tbl4 <- (addmargins(table(naps2_spink1_prss1$rs17107315_C , naps2_spink1_prss1$rs10273639_T, naps2_spink1_prss1$phenotype)))

naps2_panc_con.tbl4

fisher.test( matrix(c(9, 199, 4, 183), ncol = 2) )
fisher.test( matrix(c(46, 633, 14, 390), ncol = 2) )
fisher.test( matrix(c(32, 532, 6, 268), ncol = 2) )



naps2_cp_rap_con.tbl4 <- (addmargins(table(naps2_spink1_prss1$rs17107315_C , naps2_spink1_prss1$rs10273639_T, naps2_spink1_prss1$diagnosis)))

naps2_cp_rap_con.tbl4

```

